Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-25 paper/ms.tex
tweak plots

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in IC 2602 (the ``Southern
  Pleiades'').  The star and validated planet are therefore 30$\pm$15
  million years old.  The planet is warm ($P = 8.32\,{\rm d}$) and
  roughly Jupiter-sized.  However, its transits are grazing: $b >
  0.92$ at 3$\sigma$.  From TESS photometry alone, the planetary size
  lies within 0.58--3.87 $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$
  percentile), due to the degeneracy between the planetary size and
  the impact parameter of the transit.  From radial velocity
  monitoring, we limit the minimum mass to less than 1.20 $M_{\rm
  Jup}$ (3$\sigma$).  Grazing transits are cause for concern: they
  usually are indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Multi-color photometry requires eclipsing companions to have nearly
  identical color as TOI$\,$837, ruling out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios are limited
  by speckle imaging, but formally remain a 0.2\% possibility.  TOI
  837.01 is therefore a validated adolescent exoplanet.  Further
  observations of its stellar obliquity, atmosphere, and mass should
  confirm its planetary nature beyond doubt, and could improve our
  understanding of how the physical and orbital properties of
  exoplanets change in time.
\end{abstract}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Joint TESS and multicolor photometry.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements, detrended with a 0.3-day robust Huber spline (see
    Section~\ref{subsec:tess}).  Black points are binned to 6 minute
    intervals.  The line shows the transit model corresponding to the
    median transit parameters (Table~2).  {\it Bottom:} Multicolor
    photometry from the El Sauce 0.36m.  The consistent transit depths
    between TESS-band and the bluer Cousins-R and Johnson-B bandpasses
    rules out select false positive scenarios.
    \label{fig:jointphot}
	}
\end{figure*}

@@

\clearpage
\input{TOI837_phot_table.tex}
\input{TOI837_rv_table.tex}
\input{model_comparison_table.tex}
\input{model_posterior_table.tex}
\clearpage

>>>>

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry,
  and spectroscopy from CHIRON, FEROS, and Veloce.  We find that
  TOI$\,$837 is a $T=9.9$ G0 dwarf in IC 2602.  The star and validated
  planet are therefore between 30 and 46 million years old.  The
  planet is warm ($P = 8.32\,{\rm d}$) and roughly Jupiter-sized.
  However, its transits are grazing: $b > 0.92$ at 3$\sigma$.  From
  TESS photometry alone, the planetary size lies within 0.58--3.87
  $R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile), due to the
  degeneracy between the planetary size and the impact parameter of
  the transit.  From radial velocity monitoring, we limit the minimum
  mass to less than 1.20 $M_{\rm Jup}$ (3$\sigma$).  Grazing transits
  are cause for concern: they usually are indicative of astrophysical
  false positive scenarios.  Our follow-up data show that such
  scenarios are highly unlikely.  Multi-color photometry requires
  eclipsing companions to have nearly identical color as TOI$\,$837,
  ruling out hierarchical eclipsing binary scenarios.  Background
  eclipsing binary scenarios are limited by speckle imaging, but
  formally remain a 0.2\% possibility.  TOI 837.01 is therefore a
  validated adolescent exoplanet.  Further observations of its stellar
  obliquity, atmosphere, and mass should confirm its planetary nature
  beyond doubt, and could improve our understanding of how the
  physical and orbital properties of exoplanets change in time.
\end{abstract}

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f2b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{
    {\bf Photometry of \tn.} {\it Top:}
    Phase-folded TESS transit. Gray points are 2-minute PDCSAP flux
    measurements, detrended with a 0.3-day robust Huber spline (see
    Section~\ref{subsec:tess}).  Black points are binned to 6-minute
    intervals.  The gray line shows the median transit model corresponding to the
    fitted to both the TESS and ground-based transits
    (Table~2).  {\it Bottom:} Multicolor
    photometry from the El Sauce 0.36m; gray points are binned to 10-minute intervals.  Models
    show lower limits on the transit depths in 
    the Cousins-R and Johnson-B bandpasses used to rule out specific false positive scenarios.
    \label{fig:jointphot}
	}
\end{figure*}

@@

\clearpage
\input{TOI837_phot_table.tex}
\input{TOI837_rv_table.tex}
%\input{model_comparison_table.tex}
\input{model_posterior_table.tex}
\clearpage
